\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}

\usepackage{geometry}
\geometry{textwidth=20cm}


\title{CS131 B1: HW 6}
\author{Duy Nguyen}
\date{16 November 2016}

\begin{document}

\maketitle

\subsection*{1.}
There are 2504 CS students at a school. Of these, 1876 have taken a course in Java, 999 have
taken a course in Python, and 345 have taken a course in C++. Further, 876 have taken a courses
in both Java and Python, 231 have taken courses in both Python and C++, and 290 have taken
courses in both Java and C++. If 189 of these students have taken courses in Python, Java, and
C++, how many of these 2504 students have not taken a course in any of these three
programming languages?

The number of student who are taking at least a programming language: $1876 + 999 + 345 - 876 - 231 - 290 + 189 = 2012$.

Therefore, the number of student who aren't taking a programing language is $2054 - 2012 = 492$ students.

\subsection*{2.}
How many elements are there in the union of four sets if each of the sets has 100 elements,
each pair of the sets shares 50 elements, each three of the sets share 25 elements, and there
are 5 elements in all four sets?
\begin{center}
\begin{tabular}{r|l}
    Add all set together &  $100\cdot 4 = 400$ \\
    Minus all the pairs (6 pairs) & $- 50 \cdot 6 = 300 $\\
    Add all the triples (4 triples) & $ 25 \cdot 4 = 100$ \\
    Minus the quad & $-5$ \\ \hline
    & $195$
\end{tabular}
\end{center}
\subsection*{3.}
If the password locking TV consists of 4 digits, how many different passwords my son will have to try in the worst case to unlock the TV?

Like the iPhone old passcode lock system, 10 digits in each spot, 4 spot, so $10^4 = 10,000$.

\subsection*{4.}
 How many license plates can be made using either 3 uppercase English letters followed by 3 digits or 4 uppercase English letters followed by 2 digits?

In the first case: 3 uppercase English letters followed by 3 digits, there are $26^3 \cdot 10^3 = 17,576,000$ different plates.
In the second case: 4 uppercase English letters followed by 2 digits, there are $26^4 \cdot 10^2 = 45,697,600$ different plates.

Thus in total there are $17,576,000 + 45,697,600 = 63,273,600$ different plates.

\subsection*{5.}
There are four possibilities for each base in DNA: A, C, G, and T. How many 5-element DNA sequences of bases

a. end with A? $4^3 \cdot 1 = 64$

b. start with T and end with G? $1 \cdot 4^2 \cdot 1 = 16$

c. contain only A and T? $ 2^4 = 16$

d. do not contain C? $3^4 = 81$

\subsection*{6.}
A committee is formed consisting of one representative from each of the 50 states in the US, where a representative from a state is either the governor or one of the 2 senators from that state. How many ways are there to form this committee?

How many 50 people group you can pick out from 150 people? $$C(150,50) = \frac{150!}{50!(150-50)!}$$. 
The result is $20,128,660,909,731,932,294,240,234,380,929,315,748,140$ different ways. This looks wrong!

\subsection*{7.}
A drawer shelf contains 6 pairs of socks, each pair of a certain color (different from the rest), and all the socks are mixed on a shelf. How many individual socks should be taken from the shelf to ensure that at least 2 of them are of the same color?

$$\left \lceil{\frac{7}{6}}\right \rceil = 2$$

So at least 7 socks.

\subsection*{8.}
Show that if there are 30 students in a class, then at least 2 have the last names that begin with the same letter

There are 26 letters in the English alphabet, so if there are 27 students at least two of them will share a common first letter in their last name according to Pigeonhole principle: 
$$ \left \lceil{\frac{27}{26}} \right \rceil = 2$$. So 30 are more than enough.

\subsection*{9.}
What should be the minimum number of US students in a college to guarantee that there are at least 100 students from the same US state? 

Through the Pigeonhole principle, we have $$ \left \lceil{\frac{N}{50}} \right \rceil = 100$$. We note that $\frac{4950}{50} = 99$, so 4951 students should suffice to have at least 100 students from an US state.

\subsection*{10.}
Find the number of ways that an organization consisting of 10 members can elect a president, a
treasurer, and a secretary (one person may be elected just for one position).

$$P(10,3) = 720$$

\subsection*{11.}
Find the number of ways that an organization consisting of 10 members can elect 3
representatives to a senate

$$C(10,3) = 120$$

\subsection*{12.}
How many different strings can be made by reordering the characters of “Massachusetts”?

\begin{center}
\begin{tabular}{c|c}
    M & $C(13, 1) = 13$ \\
    a & $C(12, 2) = 66$ \\
    s & $C(10, 4) = 210$ \\
    c & $C(6, 1) = 6$ \\
    h & $C(5, 1) = 5$ \\
    u & $C(4, 1) = 4$ \\
    e & $C(3, 1) = 3$ \\
    t & $C(2, 2) = 1 $ \\ \hline
    & $64,864,800$
\end{tabular}
\end{center}

\subsection*{13.}
How many different signals, each consisting of 6 flags hung in a vertical line, can be formed from
4 identical red flags and 2 identical blue flags?

$$\frac{6!}{4!2!} = 15 $$

\subsection*{14.}
Suppose that an ice-cream café has 10 different flavors of ice cream. In how many different
ways one can choose 3 scoops of ice-cream, so that order of flavors does not matter? (There is
an unlimited amount of each flavor of ice-cream).

$C(10, 3) = 120$ different ways to scoops those ice cream.



\end{document}
